**The Heart Lies: The Role of Interoception and Theory of Mind in Deception**

### 2022-11-09 paper/manuscript.Rmd
discussion

As deception requires the liar to intentionally manipulate the beliefs of others [@burgoon1994interpersonal; @sip2012if], most research on lying capability has been focused on higher order cognitive processes, particularly in theory of mind (TOM). TOM refers to the ability to infer that others have mental states, such as beliefs, emotions and intentions, distinct from ourselves [@lee2021lying; @wellman2001meta; @baron1997mindblindness]. Indeed, the capacity to tell lies, as well as the complexity of lies told, have previously been found to be related to higher TOM abilities [@talwar2007lying; @evans2011verbal; @talwar2017role]. Furthermore, the deceptive capabilities of children is often used as a measure of their TOM abilities. However, studies investigating the links between TOM and lying ability have predominantly been focused on children and individuals with neurocognitive deficits [@beaudoin2020systematic; @bora2017meta; @roheger2022progression]; likely a result of the view of TOM as the foundation of other higher order cognitive processes [@ketelaars2010dynamics; @isaksson2021s]. As such, little is known regarding the role TOM plays in the lying ability of healthy adults.

@@

Alternatively, differences in interoception could also be a factor worthy of consideration. Broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], interoception has increasingly been tied to subjective perceptual experiences [@connell2018interoception; @seth2012interoceptive], as well as individual differences in executive functions, emotional processing and decision-making [@barrett2015interoceptive; @petzschner2021computational; @murphy2019classifying].

Given the established link between interoceptive abilities and emotional processing [@barrett2015interoceptive; @petzschner2021computational; @vabba2022interoceptive], it is possible that interoception bears influence on people's capacity to tell lies. Although there has been little research investigating the relationship between interoception and deceptive ability *per se*, some studies have found heightened self-focus towards internal bodily signals to be associated with an increased demonstration of apathetic, immoral behaviour, such as cheating [@ditto2006visceral; @williams2016valjean; @lenggenhager2013listening]. In line with these findings, @vabba2022interoceptive further reports individuals with lower interoception told significantly less egoistic lies when the social reputational stakes were high (relative to low), whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told.

In contrast, previous decision-making studies have shown a negative correlation between interoceptive awareness and one's likelihood of making risky decisions [@dunn2010listening; @furman2013interoceptive]. In fact, this is consistent with the somatic marker hypothesis, which posits interoception to be associated with a propensity towards making rational decisions [@damasio1996somatic]. While the literature pertaining to interoception seems contradictory, it is possible that these mixed findings are a result of a failure to take into consideration interoception's multidimensionality. According to @garfinkel2015knowing's three-dimensional framework, interoception is comprised of three distinct facets, namely - *interoceptive accuracy*, the objective ability to monitor internal bodily signals; *interoceptive sensibility*, the subjective confidence in one's interoceptive accuracy; and *interoceptive awareness*, the metacognitive awareness of one's interoceptive accuracy (i.e., accuracy-confidence correspondence). However, previous interoception research has largely been focused on interoceptive accuracy [@wallman2021physical]. Taking this to perspective with the paucity in studies linking deceptive ability with interoception, more studies are warranted to comprehensively examine the relationship between interoception and deception.

<!-- Interoceptive processes are not only a key component of forming your own emotions, but may also facilitate being in tune with the emotional states of others [@konvalinka2011synchronized; @garfinkel2016discrepancies]. This corresponds to situations involving deception, since much of the existing literature examining the link between interoceptive abilities has focused on how it may implicitly flag that one is being lied to through an elevated cardiac response [@gunderson2021body], and skin temperature [@van2014registered]. While research indicates that attending to ones interoceptive cues improves success in unmasking detection [@ten2019different], there is limited information how interoceptive skills may function the other way around, in the case of the liar. -->

<!-- As identified by @murphy2022propensity, the propensity to use interoceptive information, and in what manner remains an underdeveloped area in research, and may illuminate the mechanisms underlying physiological and emotional control exhibited by successful liars [@krokoszinski2016emotion; @wielgopolan2021can]. -->

@@

The aim of the present study was to explore the interplay effects of TOM and interoception on individuals' deceptive ability, as indicated by their lie confidence, physiological arousal and response time. To this end, we designed a directed-lying bi-modal feedback paradigm comprising 2 conditions ( *Interrogation* vs *Polygraph*) with distinct feedback cues. In particular, salient social feedback cues were conferred during the *Interrogation condition*, whereas physiological feedback cues were given during the *Polygraph condition*. We expected interoception to positively predict lying ability in the *Polygraph condition*, and have no significant effect on one's ability to lie in the *Interrogation condition*. Similarly, we hypothesized that TOM would positively predict individuals' capability in lying in the *Interrogation condition* and exhibit non-significant effects in the *Polygraph condition*.

@@

This study was approved by the NTU Institutional Review Board (NTU IRB-2018-10-029)(**TBC**) and all procedures performed were in accordance with the ethical standards of the institutional board and with the 1964 Helsinki Declaration. All participants provided their informed consent prior to participation and were awarded with academic credit upon completion of the study.

@@

The *Basic Empathy Scale (BES)* is a 20-item, 5-point Likert scale (Strongly Disagree - Strongly Agree) that measures cognitive and affective empathy [@jolliffe2006development]. Although TOM and empathy are regarded as distinct psychological constructs, previous research findings point to them being closely related [@gallant2020developing; @sebastian2012neural]. Specifically, empathy is often thought to be an integral component in the affective dimension of TOM (i.e., the ability to infer what someone else is feeling) [@shamay2010role]. The *Yoni Task*, which comprises 3 dimensions, namely cognitive, physical and affective, was also administered to assess participants' objective TOM ability [@shamay2007dissociable].

@@

To assess particpants' interoceptive ability, participants completed a *Heartbeat Counting Task (HCT)* [@schandry1981heart] while having their actual heartbeats recorded. During the HCT task, participants were instructed to count the number of heartbeats they felt over 5 trials with varying time intervals (20s, 25s, 30s, 35s, 40s), the sequence of which was randomized. Interoceptive accuracy (*HCT Accuracy*) was then computed based on the absolute difference between the actual number of heartbeats and the number of heartbeats counted during each trial. To assess their interoceptive sensibility (*HCT Confidence*), participants were asked to indicate, on a visual analog, how confident they were of their heartbeat counting accuracy at the end of each trial.

@@

We designed a computerized directed-lying experimental paradigm (the *Deception Task*) consisting of 2 conditions (the *Interrogation Condition* and the *Polygraph Condition*) to assess participants' lying ability.

In the **Interrogation Condition**, participants' response to each trial was followed by social feedback in the form of a video stream with an examiner. Notably, participants were informed that the examiner would be evaluating the truthfulness of their responses by observing them through the live video feed. In actuality, the video was a pre-recorded video clip of a confederate, and the same video-clip was presented to all participants.

In the *Polygraph condition*, participants' response to each trial was followed by physiological feedback in the form of an electrocardiogram (ECG) instead. Specifically, participants were informed that they were being shown live feedback of their own physiological signals when in fact, the displayed ECG was that of a pre-recorded video clip. Similar to the *Interrogation Condition*, all participants were shown the same pre-recorded video clip of an electrocardiogram.

Regardless of the task condition, participants were presented with a question, either phrased directly (*"What is your favourite sport?*), or indirectly (*"Is your favourite sport Hockey?"*), on a computer screen with accompanying instructions that either asked participants to verbally lie or tell the truth following each *Deception Task* trial. These instructions were displayed for a maximum of 10 seconds, or until the participants responded. Following each response, participants were then asked to rate their confidence in how convincing their answer was, before progressing to the next trial.

@@

In the first phase of the study, participants answered a brief demographic survey before being administered a battery of questionnaires (*BES*, *MAIA-2*, *Lie Scale*) and cognitive-behavioural tasks (*HCT*, *Yoni Task*). This series of tasks and questionnaires were administered in a randomized order [**TBC**] in order to control for order effects. In the second phase of the study, the *Deception Task* paradigm was presented to participants. Similar to the first phase, the order sequence of the 2 conditions (*polygraph* vs *interrogation*) was randomized [**TBC**], with each condition comprising 40 trials. Within each condition, participants were instructed to lie in half of the trials (20 truth trials; 20 lie trials). In total, each participant underwent 80 *Deception Task* trials, of which they had to respond with either lies or truths depending on the given instruction.

Physiological recording devices were prepared prior to beginning the experimental paradigm. Using three ECG electrodes placed according to a modified Lead II configuration [@takuma1995alternative], cardiovascular activity, sampled at 1000Hz (**TBC**) was recorded via the BioPac MP160 system (BioPac Systems Inc., USA) and the AcqKnowledge 5.0 software. Events were marked by a photosensor attached to the screen.

@@

The 8 MAIA dimensions and the 3 HCT components were reduced to 4 factors (explaining 65.17% of variance). The first factor, labelled *Interoception - Meta* (23.59%), was loaded primarily by Attention Regulation (.97), Self-regulation (.63), Emotional awareness (.60), and Noticing (.49) dimensions of the MAIA and the HCT confidence score (.40). The second factor, labelled *Interoception - Listening* (18.54%), was primarily loaded by the Body Listening (.92) and Trusting (.53) MAIA dimensions, and the Awareness (-.60) and Confidence (.46) HCT scores. The third factor, labelled *Interoception - Focus* (12.07%), was primarily loaded by MAIA Not-Distracting (.87), Emotional Awareness (-.40) and HCT Accuracy (.33). The fourth factor, labelled *Interoception - Regulation* (10.97%), was primarily loaded by MAIA not-worrying (.71), HCT Accuracy (.61) and MAIA Trusting (.40). However, due to the interpretation difficulty, we will refer to these dimensions with their main correlates in **Figure 1**.

@@

While there is extensive literature associating deception with social cognition and emotion regulation, most of such research had been focused on deception detection, leaving a paucity in the studies pertaining to lying ability. This study hence seeks to address this research gap, further aiming to examine the interplay effect of TOM and interoception on deceptive ability. Using a bi-modal feedback deception task paradigm, participants were found to report significantly lower lie confidence in the *Polygraph condition*, relative to the *Interrogation condiiton*. Notably, we also found a significant association between several facets of interoception with individuals' lie confidence and response time in the polygraph condition. Taken together, this could be suggestive of people's greater reliance on social feedback cues when telling lies

<!-- Participants relied on interoception -->

Our results show that participants who were telling the truth had a slower reaction time, and rated themselves as less confident in the polygraph condition, however, their heart rate averaged lower as compared to the interrogation condition. This suggests that despite the participant's lack of confidence, they were very in-tune with their physiological response in the polygraph condition, and successfully able to decrease their heart rate. Given that interoceptive accuracy is enhanced by focusing on it during a time of stress [@schulz2013cold], such as attempting to conceal deception combined with false physiological feedback delivered during the polygraph condition, this conclusion is in line with our hypothesis.

As the relationship between interoception and emotion is well established [@barrett2015interoceptive; @dobrushina2020interaction; @ohira2020predictive], our work is consistent with @wielgopolan2021can, who found that groups with higher emotional awareness made better liars and were more successful at regulating their emotional and physiological responses, as well as fabricating new ones.

<!-- Metacognition and Interoception -->

Although participants were not explicitly directed to attend to their physiological signals as a means of evading deception detection, they were aware these signals were recorded and informed that their lies would be detected through their analysis. Additionally, the presence of the ECG likely made them aware, and these measures remained connected during the interrogation. This indicates that there was likely an explicit attentional component to the control exerted, which is further reflected by a broader theme in our results. Our results indicate that all interoceptive factors (*Meta, Listening, Focus and Regulation*) are associated with an increased confidence in deceptive abilities, and faster reaction time for lies in the polygraph condition. It logical that confidence in deception would be accompanied by faster reaction time. However, since confidence was a subjective measure, it does not necessarily reflect competence [@khalsa2008interoceptive]. While our data indicates that participants were able to self-regulate using interoceptive abilities, this still highlights an important caveat, which is the potential metacognitive awareness at play [@garfinkel2015knowing].

Metacognitive beliefs, or interoceptive awareness about competence in the quality of physiological regulation may influence the cognitive processes and development physiological responses. That is to say, that the appraisal is just as important to the process of deception by informing their true ability [@stephan2016allostatic; @harrison2021filter; @petzschner2021computational].

<!-- Interoceptive sensibility and risk-taking -->

High interoceptive sensibility regardless of true competence may also directly shape behaviour through the reduced perception of risk associated with being caught. Past research indicates the likelihood of deception increases when individuals judge a lower risk of being caught, based on situation-specific variables and their own qualities [@sip2012if; @sip2013pinocchio]. These results may offer support to findings such as @vabba2022interoceptive where interoceptive abilities were found to be a significant moderator in the willingness to engage in riskier forms of deception, and offer insight into other risk behaviours linked with interoceptive ability such as cheating [@williams2016valjean] and risk-taking [@ditto2006visceral; @lenggenhager2013listening].

<!-- Future Research -->

>>>>

As deception requires the liar to intentionally manipulate the beliefs of others [@burgoon1994interpersonal; @sip2012if], most research on lying capability has been focused on higher order cognitive processes, particularly in theory of mind (TOM). TOM refers to the ability to infer that others have mental states, such as beliefs, emotions and intentions, distinct from ourselves [@lee2021lying; @wellman2001meta; @baron1997mindblindness]. Indeed, the capacity to tell lies, as well as the complexity of lies told, have previously been found to be related to higher TOM abilities [@talwar2007lying; @evans2011verbal; @talwar2017role]. Furthermore, the deceptive capabilities of children is often used as a measure of their skills in TOM. However, studies investigating the links between TOM and lying ability have predominantly been focused on children and individuals with neurocognitive deficits [@beaudoin2020systematic; @bora2017meta; @roheger2022progression]; likely a result of the view of TOM as the foundation of other higher order cognitive processes [@ketelaars2010dynamics; @isaksson2021s]. As such, little is known regarding the role TOM plays in the lying ability of healthy adults.

@@

Alternatively, interoceptive abilities could also influence inter-individual differences in lying. Broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], @garfinkel2015knowing's conceptualizes interoception as a three-dimensional framework comprising three distinct facets, namely - *interoceptive accuracy*, the objective ability to monitor internal bodily signals; *interoceptive sensibility*, the subjective confidence in one's interoceptive accuracy; and *interoceptive awareness*, the metacognitive awareness of one's interoceptive accuracy (i.e., accuracy-confidence correspondence). Interoception has increasingly been tied to subjective perceptual experiences [@connell2018interoception; @seth2012interoceptive], as well as individual differences in executive functions, emotional processing and decision-making [@barrett2015interoceptive; @petzschner2021computational; @murphy2019classifying]. Although little research interest has been conferred to investigating the relationship between interoception and deceptive ability *per se*, previous decision-making studies have demonstrated a negative correlation between interoceptive awareness, a metacognitive dimension of interoception, and one's likelihood to make risky decisions [@dunn2010listening; @furman2013interoceptive]. In fact, this is consistent with the somatic marker hypothesis, which posits interoception is associated with a propensity towards making rational decisions [@damasio1996somatic].

In contrast, some studies have instead found heightened interoceptive attention, one's self-focus towards internal bodily signals, to predict apathetic, immoral behaviour, such as cheating [@ditto2006visceral; @williams2016valjean; @lenggenhager2013listening]. Extending these findings to social cognition, @vabba2022interoceptive further reports individuals with lower interoception told significantly less egoistic lies when the social reputational stakes were high (relative to low), whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told.

While the literature pertaining to interoception seems contradictory, it is possible that these mixed findings are a result of a failure to take into consideration interoception's multidimensionality. Indeed, previous interoception research has largely been focused on examining interoceptive accuracy [@wallman2021physical]. Taking this to perspective with the paucity in studies linking deceptive ability with interoception, more studies are warranted to comprehensively examine the relationship between interoception and deception.

@@

The aim of the present study was to explore the interplay effects of TOM and interoception on individuals' deceptive ability, as indicated by their lie confidence, physiological arousal and response time. To this end, we designed a directed-lying bi-modal feedback paradigm comprising 2 conditions ( *Interrogation* vs *Polygraph*) with distinct feedback cues. In particular, salient social feedback cues were conferred during the *Interrogation condition*, whereas visual biofeedback cues were given during the *Polygraph condition*. We expected interoception to positively predict lying ability in the *Polygraph condition*; participants with better interoception would exhibit higher lie confidence, shorter response time and lower physiological arousal. Alternatively, we hypothesized TOM would positively predict individuals' capability in lying in the *Interrogation condition*.

@@

This pre-registered study (**OSF?**) was approved by the NTU Institutional Review Board (NTU IRB-2018-10-029)(**TBC**) and all procedures performed were in accordance with the ethical standards of the institutional board and with the 1964 Helsinki Declaration. All participants provided their informed consent prior to participation and were awarded with academic credit upon completion of the study.

@@

The *Basic Empathy Scale (BES)*, a 20-item, 5-point Likert scale (Strongly Disagree - Strongly Agree) that measures cognitive and affective empathy [@jolliffe2006development] was administered. Although TOM and empathy are regarded as distinct psychological constructs, previous research findings point to them being closely related [@gallant2020developing; @sebastian2012neural]. Specifically, empathy is often thought to be an integral component in the affective dimension of TOM (i.e., the ability to infer what someone else is feeling) [@shamay2010role]. The *Yoni Task*, which comprises 3 dimensions, namely cognitive, physical and affective TOM, was also administered to assess participants' objective TOM ability [@shamay2007dissociable].

@@

To assess participants' interoceptive ability, participants completed a *Heartbeat Counting Task (HCT)* [@schandry1981heart] while having their actual heartbeats recorded. During the HCT task, participants were instructed to count the number of heartbeats they felt over 5 trials with varying time intervals (20s, 25s, 30s, 35s, 40s), the sequence of which was randomized. Interoceptive accuracy (*HCT Accuracy*) was then computed based on the absolute difference between the actual number of heartbeats and the number of heartbeats counted during each trial. To assess their interoceptive sensibility (*HCT Confidence*), participants were asked to rate, on a visual analog, how confident they were of their heartbeat counting accuracy at the end of each interval.

@@

We designed a directed-lying bi-modal feedback task (the *Deception Task*) consisting 2 conditions - namely, the *Interrogation* condition and the *Polygraph* condition.

In the *Interrogation* condition, participants were given social feedback in the form of a video stream with an examiner. Notably, participants were informed that the examiner would be evaluating the truthfulness of their responses by observing them through the live video feed. In actuality, the video was a pre-recorded video clip of a confederate, and the same video-clip was presented to all participants.

In the *Polygraph* condition, participants were given biofeedback in the form of an electrocardiogram (ECG) displayed onscreen instead. Specifically, participants were informed that they were being shown live feedback of their own heartbeats when in fact, the displayed ECG was that of a pre-recorded video clip. Similar to the *Interrogation* condition, all participants were shown the same pre-recorded video clip of the ECG.

The sequence of each task trial was the same for both conditions. Using a computer, participants were first shown a question, either phrased directly (*"What is your favourite sport?*), or indirectly (*"Is your favourite sport Hockey?"*), with accompanying instructions below that either asked participants to verbally lie or tell the truth. Following a connecting screen (0.7 - 1.5s), participants were presented with either social (*Interrogation* condition) or biofeedback (*Polygraph* condition) that was displayed for a maximum of 10s or until they made their accorded response. A disconnecting screen was then displayed (1.5-2.5s), following which participants were asked to rate their confidence in how convincing they perceived their answer to be.

@@

In the first phase of the study, participants answered a brief demographic survey before being administered a battery of questionnaires (*BES*, *MAIA-2*, *Lie Scale*) and cognitive-behavioural tasks (*HCT*, *Yoni Task*). This series of tasks and questionnaires were administered in a randomized order [**TBC**] in order to control for order effects. In the second phase of the study, the *Deception Task* was conducted using PsychoPy [**REF**]. Each participant was conferred both conditions of the *Deception Task*, the order sequence of which was randomized. Each task condition comprised 40 trials, of which participants were instructed to lie in half of the trials (20 **Truth** trials; 20 **Lie** trials). In total, each participant underwent 80 *Deception Task* trials.

Physiological recording devices were prepared prior to beginning the experimental paradigm. Using three ECG electrodes placed according to a modified Lead II configuration [@takuma1995alternative], cardiovascular activity, sampled at 1000Hz (**TBC**) was recorded via the BioPac MP160 system (BioPac Systems Inc., USA) and the AcqKnowledge 5.0 software.

@@

The 8 MAIA dimensions and the 3 HCT components were reduced to 4 factors (explaining 65.17% of variance). The first factor, labelled *Interoception - Meta* (23.59%), was loaded primarily by Attention Regulation (.97), Self-regulation (.63), Emotional awareness (.60), and Noticing (.49) dimensions of the MAIA and the HCT confidence score (.40). The second factor, labelled *Interoception - Listening* (18.54%), was primarily loaded by the Body Listening (.92) and Trusting (.53) MAIA dimensions, and the Awareness (-.60) and Confidence (.46) HCT scores. The third factor, labelled *Interoception - Focus* (12.07%), was primarily loaded by MAIA Not-Distracting (.87), Emotional Awareness (-.40) and HCT Accuracy (.33). The fourth factor, labelled *Interoception - Regulation* (10.97%), was primarily loaded by MAIA not-worrying (.71), HCT Accuracy (.61) and MAIA Trusting (.40). However, due to the interpretation difficulty, we will refer to these dimensions with their main correlates in **Figure 1** [**Note to fix caption for Figure 1 from HCT Trusting to MAIA trusting**].

@@

While there is an extensive body of literature associating deception with social cognition and emotion regulation, most research had been focused on their roles in deception detection, leaving a paucity in studies pertaining to their influence on lying ability. The present study hence seeks to address this research gap, further aiming to examine the interplay effect of TOM and interoception on our ability to lie convincingly. Notably, we found a significant difference in participants' lying ability (as measured by response time, heart rate and confidence ratings) between the *Polygraph* and *Interrogation* conditions. This hence confers support for the manipulation used in our experimental paradigm, demonstrating that increasing the attentional focus towards external (visual) interoceptive cues can enhance interoceptive sensitivity, therefore improving the precision of internal signals perceived. Extending the growing body of literature pertaining to the application of interoceptive training to improve emotion regulation [@sugawara2020effects; @quadt2021interoceptive; @wu2022enhanced], our study thus provides evidence that interoceptive sensitivity can be manipulated and thereby modified to guide our emotional responses.

<!-- Interoceptive vs Social Cues -->
Using a bi-modal feedback deception task, we found partial support for our hypothesis. Specifically, participants reported lower lie confidence and took a longer time to respond, but were less physiologically aroused in the *Polygraph* condition, relative to the *Interrogation* condition. While this mixed finding is challenging to interpret, it is possible that one's interoceptive sensitivity, enhanced by the perceived interoceptive cues, interacted with the stress experienced in such deceptive interactions and led to a depletion of cognitive resources [@ten2015physically; @porter2012secrets]. Indeed, the experience of excessive stress has been shown to impair interoceptive accuracy, leading to a hyper-focus on internal bodily signals [@schulz2015interoception]. Furthermore, this is also in line with the established attentional switching hypothesis, which posits that an increase in attention towards internal signals and managing one's emotional reaction would confer less cognitive resources available for the actual act of telling a lie, thereby resulting in individuals taking a longer time to respond, and rating their lies with less confidence [@arnold2019interoception; @hanania2010selective]. This interplay of interoception and maladaptive stress response, and their effect on lying ability hence underscores the complexity underlying successful deceptive behaviour.

<!-- Meta-Interoception, Emotion Regulation and Lying -->
Consistent with our hypothesis, a significant positive association was predominantly found between metacognitive dimensions of interoception (*Meta* and *Regulation* interoception) and individuals' lie confidence when their physiological cues were salient. In contrast to previous studies [@pinna2020systematic; @fustos2013embodiment; @owens2018investigating; @pollatos2007heart], we did not find any significant relationship between individuals' interoception scores and objective heart rate. Taken together, these findings suggest that interoceptive awareness, in and of itself, is insufficient for adaptive emotion regulation. Indeed, some researchers have found positive links between interoceptive awareness and individuals' use of maladaptive strategies such as rumination [@tan2023interoceptive]. Furthermore, hypervigilance to bodily signals is also positively related to somatization and psychopathological disorders such as anxiety [@wang2020intrinsic; @dunn2010can; @pollatos2007interoceptive]. As such, further studies are necessary to examine what factors modulate the relationship between the metacognitve facets of interoception and emotion regulation.

<!-- TOM -->
Our results show a significant association between individuals' composite TOM score with lower lie confidence and longer response times when interoceptive cues were highly salient. Recent studies linking interoceptive abilities and social cognition with one's experience of self posit that an accurate sense of internal bodily signals is integral for individuals to maintain a distinction between self and other, while correctly inferring the mental states of others [@shah2017heart; @palmer2018going]. Taking this to perspective with the predictive coding framework [@friston2010free], when interoceptive cues are highly salient, the resulting increase in interoceptive awareness will be conflicted against higher (more precise) exteroceptive TOM. To attenuate this conflict so as to maintain balance between our interoceptive and exteroceptive states, it is hence possible that individuals experienced a re-direction of their attentional resources from external to internally-focused signals to update higher order beliefs. Consistent with the attentional shift hypothesis [@arnold2019interoception; @hanania2010selective], this re-direction of cognitive resources away from that needed to convincingly tell a lie could thus have led to lower lie confidence and a longer response time.

<!-- Potential Implications  -->

<!-- Limitations and Future Research -->
- NOTE: no significant correlation between HCT accuracy and MAIA dimensions (only HCT confidence sig correlates with MAIA dimensions of awarenss and regulation)
